Data Management \\ and LSST Special Programs

### 2021-11-28 DMTN-065.tex
removed refs to 2018 white papers

The main LSST science goals will be met by the Wide-Fast-Deep (WFD) Main Survey, but this is expected to be accomplished with $85$--$90$\% of the observing time available over the $10$ year survey.
The remaining $10$--$15$\% of the time will be spent on Special Programs: alternative survey areas and/or observing strategies driven by a specific science goal.
%A call for white papers that provide scientific motivation and observing strategies for the WFD survey and Special Programs, \citeds{Document-28382}, released in June 2018, has a deadline of November 30 2018.
It is conceivable that Special Programs might obtain imaging data that are significantly different from the WFD main survey, and/or requires special processing in order to achieve the program's science goals.
This document provides an in-depth description of the role of the LSST Project in preparing to process the data from Special Programs (expanding on the general description in Section 6 of \citeds{LSE-163}).
The main target audience is the LSST Data Management (DM) team, but members of the science community who are preparing white paper proposals may also find this document useful.

@@

If the user-generated processing pipeline for Special Programs data requires requires significantly more computational resources than have been allocated -- where that allocation has been sized approximately, based on image processing for WFD main survey data (i.e., difference imaging, source detection, and/or stacking) -- then external computational resources may be necessary.
To support such external processing DM intends to make the data and its code base accessible to and exportable by users in the science community.

No user-generated pipeline may contribute Alerts to the Alert Stream, although a separate stream should be possible if the packet and transport formats are adopted (see also Section \ref{ssec:dmplans_user}).

@@

For further insight to the DM-related needs of potential Special Programs, we can write out all of the data acquisition and processing steps, in order, that some of the proposed Special Programs might use. This kind of thought experiment of describing the reductions and processing could also be a required section of all future white paper proposals. Note that we are not including any analysis in these descriptions, only processing and products. These are not necessarily complete and may even be incorrect in some places, as we are not experts in the science needs of these potential Special Programs; they could use some more thought and input.

>>>>

The main LSST science goals will be met by the Wide-Fast-Deep (WFD) Main Survey, but this is expected to be accomplished with $85$--$90$\% of the observing time available over the $10$ year survey.
The remaining $10$--$15$\% of the time will be spent on Special Programs: alternative survey areas and/or observing strategies driven by a specific science goal.
%A call for white papers that provide scientific motivation and observing strategies for the WFD survey and Special Programs, \citeds{Document-28382}, released in June 2018, has a deadline of November 30 2018.
It is conceivable that Special Programs might obtain imaging data that are significantly different from the WFD main survey, and/or requires special processing in order to achieve the program's science goals.
This document provides an in-depth description of the role of the LSST Project in preparing to process the data from Special Programs (expanding on the general description in Section 6 of \citeds{LSE-163}).
The main target audience is the LSST Data Management (DM) team, but members of the community who are planning to use Special Programs to reach their science goals may also find this document useful.

@@

If the user-generated processing pipeline for Special Programs data requires requires significantly more computational resources than have been allocated -- where that allocation has been sized approximately, based on image processing for WFD main survey data (i.e., difference imaging, source detection, and/or stacking) -- then external computational resources may be necessary.
To support such external processing DM intends to make the data and its code base accessible to and exportable by users in the science community.
No user-generated pipeline may contribute Alerts to the Alert Stream. %, although a separate stream should be possible if the packet and transport formats are adopted (see also Section \ref{ssec:dmplans_user}).

@@

For further insight to the DM-related needs of potential Special Programs, we can write out all of the data acquisition and processing steps, in order, that some of the proposed Special Programs might use.
Note that we are not including any analysis in these descriptions, only processing and products. These are not necessarily complete and may even be incorrect in some places, as we are not experts in the science needs of these potential Special Programs; they could use some more thought and input.
